Dynamics of the Lower Solar Atmosphere

### 2024-07-23 chapter3/ms.tex
Updates from Overleaf

%-----------------------------------------------------------
\begin{table*}[ht!]
\begin{center}
\begin{tabular}{||l|c|c|c|r||}
\hline
\textbf{Science}  &	\textbf{Combination} &	\textbf{Central} & \textbf{Bandpass} &\textbf{Science} \\
\textbf{Filter}	&	\textbf{Filter}     &	\textbf{Wavelength  (nm)}	&		\textbf{(nm)	}	   	&\textbf{target}		\\
\hline
NB01     & BB01 		& 214.0 		    & 11.0 		& Continuum\\
NB02 	& BP02		& 276.7				& 0.4 		& Mg~\rm{II}~k blue wing \\
NB03 	& BP02		& 279.6 			& 0.4 		& Mg~\rm{II}~k\\
NB04 	& BP02		& 280.3				& 0.4 		& Mg~\rm{II}~h\\
NB05		& BP02		& 283.2				& 0.4 		& Mg~\rm{II}~h red wing\\
NB06 	& BP03		& 300.0 			&1.0 		& Continuum\\
NB07 	& BP03		& 388.0				&1.0 		& CN Band\\
NB08		& NB08		& 396.85 			& 0.1 		& Ca~\rm{II}~h\\
BB01 	& BB01		& 220.0				& 40.0		& Herzberg Continuum \\
BB02 	& BP04		& 277.0 			& 58.0       & Hartley Band\\
BB03 	& BP04		& 340.0				& 40.0        & Huggins Band\\
\hline
\end{tabular}
\end{center}
\caption{List of science filters on board \suit. Columns from left to right denote filter mnemonics (including science and combination filters; NB: Narrowband, BB: Broadband, BP: Bandpass), central wavelengths for science filters and corresponding bandpasses, and the observation interest for the filter.} 
\label{tab:science_filters}
\end{table*}
%-----------------------------------------------------------

>>>>

%-----------------------------------------------------------
\begin{table*}[ht!]
\begin{center}
\begin{tabular}{||l|c|c|c|r||}
\hline
\textbf{Science}  &	\textbf{Combination} &	\textbf{Central} & \textbf{Bandpass} &\textbf{Science} \\
\textbf{Filter}	&	\textbf{Filter}     &	\textbf{Wavelength  (nm)}	&		\textbf{(nm)	}	   	&\textbf{target}		\\
\hline
NB1     & BB1 		& 214.0 		    & 11.0 		& Continuum\\
NB2 	& BP2		& 276.7				& 0.4 		& Mg~\rm{II}~k blue wing \\
NB3 	& BP2		& 279.6 			& 0.4 		& Mg~\rm{II}~k\\
NB4 	& BP2		& 280.3				& 0.4 		& Mg~\rm{II}~h\\
NB5		& BP2		& 283.2				& 0.4 		& Mg~\rm{II}~h red wing\\
NB6 	& BP3		& 300.0 			&1.0 		& Continuum\\
NB7 	& BP3		& 388.0				&1.0 		& CN Band\\
NB8		& NB8		& 396.85 			& 0.1 		& Ca~\rm{II}~h\\
BB1 	& BB1		& 220.0				& 40.0		& Herzberg Continuum \\
BB2 	& BP4		& 277.0 			& 58.0       & Hartley Band\\
BB3 	& BP4		& 340.0				& 40.0        & Huggins Band\\
\hline
\end{tabular}
\end{center}
\caption{List of science filters on board \suit. Columns from left to right denote filter mnemonics (including science and combination filters; NB: Narrowband, BB: Broadband, BP: Bandpass), central wavelengths for science filters and corresponding bandpasses, and the observation interest for the filter.} 
\label{tab:science_filters}
\end{table*}
%-----------------------------------------------------------
